% Chapter 1

\chapter{INTRODUCTION} % Write in your own chapter title All Chapter headings in CAPS
\section{Problem Domain}

\section{Problem Statement} % All Section headings in Title Case
Nowadays digital video plays an important role in every day’s life and due to widely used low cost storage media, the volume of digital video tends to be very large and variety of available video data makes the search and retrieval of content a more and more difficult task. The amount of information generated in today’s society is growing exponentially. Video images are voluminous, redundant and their overall contents cannot be captured at a glance. It is essential to help user to provide more compact, interesting video content with narrow bandwidth. In order to meet this need, video summarization is needed. A complete sports video whose duration is much longer like cricket is monotonous which most viewers don’t prefer. Hence Sports Highlights extraction was brought to light. This work generates highlights of cricket match video.
\section{Challenges}%All Sub Section headings in Title Case
\subsection{Match Timing}
The day time match will have high contrast and night match will have low contrast. This variations affects recognition of the scorecard. 
\subsection{Event Detection}
Event detection for every frame in the cricket match is highly challenging. If not classified properly, it affects further classification in the highlights.
\subsection{Replays and Advertisements}
Key events like  Wicket, Six, Four etc in Cricket Match are followed by replay of that event. This replay are the repetitive video shot of the actual event.
\section{Contributions} %All Sub Section headings in Title Case
\begin{enumerate}
    \item \textbf{Problem:} Given a cricket video match, generate highlights video.
    
    We propose a system that identifies the highlights in the input video.
    \item \textbf{Problem:} Given a cricket video match with advertisements and replays,Identify these events.
    
    We propose a method that classifies the video as advertisements and replay or live frames.
\end{enumerate}
