% Chapter 3

\chapter{REQUIREMENTS ANALYSIS} % All Chapter Headings in ALL CAPS

\section{Functional Requirements}
The system outputs the highlights video for a given Cricket input video. The output video should adhere to the following requirements:
• The output video should contain all the key events such as wickets, boundaries and other excitement events
• The system must be able to detect the presence and absence of scorecard in the vide
• The output video should not contain replays/ ad
• The system must be optimized for time and space complexities
• The system must be able to classify the input video and annotate with its events
\section{Non Functional Requirements}
\subsection{User Interface}
There must be a simple and easy to use user interface.
The intermediate results such as video classification, OCR results are printed in the CSV file for easy perception.
The output video clips are concatenated and stored in a new output file by using movie editing tools.
\subsection{Hardware}
A system capable of running a python program with a minimum of 2GB RAM is required.
\subsection{Software}
• Operating System: Windows
• Programming Language: Python
• Tools: Opencv, Keras, Moviepy, Pytesseract.
\subsection{Performance}
The system must be optimized, reliable, consistent and available all
the time.

\section{CONSTRAINTS AND ASSUMPTIONS}
\subsection{Constraints}
•The system would work only for the BBL Cricket match videos.
More than 2500 images are generated manually for CNN classification inorder to attain better results.
•The output video will work effectively only when BBL cricket match video 
•If the input video doesn't contain the key events as per the precoded criteria No output video will be generated.
•The Accuracy of the system is calculated only by the analysis of confusion matrix.

\subsection{Assumptions}
• The Fours/Sixes, wickets and excitement shots are the only highlights
• All the key events are detected only by analysing the scorecard and the audio.
• OCR detects and recognizes all tha scorecards effectively
• The Scorecard will display the exact score of that particular delivery without any errors.