% Chapter 3

\chapter{REQUIREMENTS ANALYSIS} % All Chapter Headings in ALL CAPS

\section{Functional Requirements}
The system outputs the highlights video for a given cricket video input. The output video should adhere to the following requirements:
\begin{itemize}
\item The output video should contain all the key event segments such as wickets, boundaries.
\item he output video should contain all the video segments containing excitement.
\item The system must be able to detect the presence and absence of scorecard in the input video.
\item The output video should not contain replays/advertisements segments.
\item The system must be able to classify the input video frames and annotate each frame with the event associated with it.
\item The system must be optimized for the time and space complexities.
\end{itemize}

\section{Non Functional Requirements}
\subsection{User Interface}
There must be a simple and easy to use user interface.
The intermediate results such as video classification, OCR results are printed in the CSV file for easy perception.
The output video clips are concatenated and stored in a new output file by using movie editing tools.
\subsection{Hardware}
A system capable of running a python program with a minimum of 2GB RAM is required.
\subsection{Software}
\begin{itemize}
\item Operating System: Windows
\item Programming Language: Python
\item Tools: Opencv, Keras, Moviepy, Pytesseract.
\end{itemize}

\subsection{Performance}
The system must be optimized, reliable, consistent and available all
the time.

\section{Constraints and Assumptions}
\subsection{Constraints}
\begin{itemize}
\item The system would work effectively only for the BBL Cricket match videos.
\item More than 4000 images are captured manually for CNN classification in order to attain better results.
\item The crucial events such as last over balls may not be detected by using the scorecard recognition and excitement.
\item The match winning overs will have too much of excitement even for non key events and it is difficult to distinguish the ball segments with excitement.
\item If the input video doesn't contain the key events as per the pre coded criteria, No output video will be generated.
\item The Accuracy of the system is calculated only by the analysis of confusion matrix.
\end{itemize}
\subsection{Assumptions}
\begin{itemize}
    \item The fours, sixes, wickets and those shots containing commentators excitement and crowd cheers are the only highlights
    \item The fours, sixes and wickets can be classified by using the scorecard alone
    \item All the key events are detected only by analyzing the scorecard and the audio.
    \item OCR detects and recognizes all the scorecards effectively
    \item The Scorecard will display the exact score of that particular frame without any typos.
\end{itemize}

